---
title: "Getting Started with binomial"
author: "Hyungil Shim"
date: "May 3, 2019"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

# Binomial

The package `binomial` allows the user to explore the binomial distribution model through functions and plots that help contextualize and visualize a binomial random variable.

# Creating a `binvar`

Start off by creating a binomial random variable with class `binvar` with the `bin_variable()` function

```{r}
bin1 <- bin_variable(trials = 10, prob = 0.5)
bin1

class(bin1)
```
As you can see, we have created an object `bin1` with class `binvar`

# Using `summary` on `binvar` objects

You can use the summary function to view important data points for a given `binvar` object
```{r}
summary(bin1)
```
You can use other main functions to calculate individual data points
```{r}
# mean
bin_mean(trials = 10, prob = 0.5)

# variance
bin_variance(trials = 10, prob = 0.5)

# mode
bin_mode(trials = 10, prob = 0.5)

# skewness
bin_skewness(trials = 10, prob = 0.5)

# kurtosis
bin_kurtosis(trials = 10, prob = 0.5)
```

# Data Visualization
There are two main way of visualizing the binomial distribution with this package: plotting with `bin_distribution` or `bin_cumulative`

`bin_distribution` finds the probabilities of each additional success into an object `bindis`. You can then plot this object.

`bin_cumulative` is similar to `bin_distribution`, but it includes another column that adds up each probability in to an object `bincum`. You can then plot this object.
```{r}
dis1 <- bin_distribution(trials = 10, prob = 0.5)
dis1
plot(dis1)

cum1 <- bin_cumulative(trials = 10, prob = 0.5)
cum1
plot(cum1)
```
